Airline Customer Satisfaction - Group 17

### 2025-03-27 Draft Business Analytics Assignment Group 17 (1).Rmd

>>>>

In this project, Group 17 serves as business consultants, with a focus on improving customer experience in the industry. Our responsibilities are from analyzing customer satisfaction statistics, developing measures to improve the airline's overall performance. Therefore, the business problem that we solve is "how the airline can improve its strategy of services and activities to significantly increase customer satisfaction, especially between segments and main service areas, thus promoting customer loyalty and achieving stronger competitive advantages?".

 The reason why we chose airline industry as our focus

 We provide comprehensive data from Kaggle across various aspects of the flying experience which allows us to in-depth analysis.

Intense rivalry airline industry has intense competition among company, and it could be easily justified by customer satisfaction. Thus, higher customer satisfaction leads to increased client retention and overall business performance.

Concentrating on major market segments may be an efficient technique for improving overall consumer satisfaction.

Why focus on customer satisfaction?

Enhance customer loyalty: improving on these key segments and service areas will enhance customer satisfaction that potentially increases customer loyalty rate.

Competitive Advantage: by addressing the service issue, the airline can stand out from the competitors.
